\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-20 paper/main.tex
.

\subsection{Protein-centric evaluation}
The goal of \name is to find candidate drugs that target a specific
protein; however, our evaluation does not evaluate this application
but rather how \name would perform in finding plausible drug--target
interactions among all possible interactions. To provide a better
estimate on how \name performs for individual protein targets, we use
micro-averages between proteins and compute the \textit{MicroAUC} (see
Section \ref{sec:evaluation}); micro-averages average the performance
(true and false positive rates) per protein instead of across all
drug--protein pairs, and can therefore better estimate how \name
performs when tasked with finding a drug that targets a specific
protein.

>>>>

\subsection{Protein-centric evaluation}
The goal of \name is to find candidate drugs that target a specific
protein; however, so far, we do not evaluate this application
but rather how \name would perform in finding plausible drug--target
interactions among all possible interactions. This evaluation does not
correspond to the application of \name in finding drugs that target a
specific protein.
To provide a better
estimate on how \name performs for individual protein targets, we use
micro-averages between proteins and compute the \textit{MicroAUC} (see
Section \ref{sec:evaluation}); micro-averages average the performance
(true and false positive rates) per protein instead of across all
drug--protein pairs, and can therefore better estimate how \name
performs when tasked with finding a drug that targets a specific
protein.
